Simple models of deliberated preference

### 2018-01-27 simple.tex
Various impr

\RequirePackage[l2tabu, orthodox]{nag}
\RequirePackage{silence}\WarningFilter{typearea}{Maybe no optimal type area settings}
\documentclass[version=last, pagesize, twocolumn, twoside=off, bibliography=totoc, 12pt, a4paper, french, english]{scrartcl}
\input{preamble/packages}
\input{preamble/math_basics}
\input{preamble/math_mine}
\input{preamble/redac}
\input{preamble/draw}
\input{preamble/acronyms}
\addtokomafont{labelinglabel}{\sffamily\bfseries}

%printer margin: I take 0.5 inches = 1,27 cm to be safe. 21 cm - (2 × 1.27 cm) = 18.46 cm. 29.7 cm − 0.9 cm − (2 × 1.27 cm) = 26.26 cm
\areaset{18.46cm}{26.26cm}
\setlength{\footskip}{9mm}
\begin{document}
\title{Simple models of deliberated preference}
\author{Olivier Cailloux}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

@@

We define two binary relations $\prop^+$ (always supports $\propposs$) and $\prop^−$ (always supports $¬\propsure$) on $\allargs$. We define $(\ar, \ar') \in \prop^+ ⇔ (\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
Hence, $(\ar, \ar') \notin \prop^+ ⇔ (\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \notin \prop^− ⇔ (\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.

@@

Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on, together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.} 
and (A2) that $\ileadstosst \subseteq \ileadstopst$ 
\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}
and the fact that the relations $\prop^+$ and $\prop^−$ are symmetric. 
\footnote{Unclear where we use the fact that the relations $\prop^+$ and $\prop^−$ are symmetric.}

We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.

@@

We say that severe $\prop$-unstability happens iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
\footnote{Severe $\prop$-unstability happens iff severe $¬\prop$-unstability happens.}
\footnote{Here is an example of severe $\prop$-unstability. $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}

\begin{theorem}
	If $\prop \notin \iposs ∧ ¬\prop \notin \iposs$, severe $\prop$-unstability happens.
\end{theorem}
The proof follows from \cref{ft:notposs}.

\begin{theorem}
	$\prop \in \isure ⇒ ¬\prop \notin \iposs$.
\end{theorem}
This is because $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).

@@

\begin{definition}[Clear-cut]
	A situation is $\prop$-clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
\footnote{Here is an example of non $\prop$-clear-cut situation with no severe $\prop$-unstability. $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstope \prop, (\ar, \ar') \ileadstopst ¬\prop$.}
\footnote{Something like Axiom JU should be sufficient for CC. JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive. Means that if not CC, then not JU. Hence, infinite discussion happens, or irreducible unstability. Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.}
\end{definition}

\subsection{Possible outcomes}
We know $\prop \in \isure ⇒ ¬\prop \notin \iposs$ and $\prop \in \isure ⇒ \prop \in \iposs$.

Here are the remaining possibilities, considering the four pairs $(\prop, \iposs)$, $(\prop, \isure)$, $(¬\prop, \iposs)$, $(¬\prop, \isure)$. (A pair $(\prop, T)$ not mentioned means $\prop \notin T$.)
\begin{labeling}{Unstability, $¬\prop$ poss}
	\item[All poss] $\prop \in \iposs$, $¬\prop \in \iposs$
	\item[$\prop$ sure] $\prop \in \iposs$, $\prop \in \isure$
	\item[$¬\prop$ sure] (symmetric)
	\item[Unstability, $\prop$ poss] $\prop \in \iposs$ (oddity: $¬\prop \notin \iposs$ should imply $\prop \in \isure$)
	\item[Unstability, $¬\prop$ poss] (symmetric)
	\item[Strong unstability] (both oddities above)
\end{labeling}

\section{Models}
A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the constraints as indicated here.

@@

Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$. We write $\args \mbeats \ar$ to mean that $\forall \ar' \in \args: \ar' \mbeats \ar$, and similarly for other binary relations.

Given a decision situation, define $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ as follows.

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ (\ar_3, \ar_2) \ileadstope ¬\prop$.}

@@

This is well defined thanks to the following construction.
Given a model. 
\begin{itemize}
	\item Define a root as an argument that $\mbeats$-attacks nobody. 
	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$ (thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on). 
	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. %as $\ar_3 \wibeatse[\prop]_{(1)} \ar_2$ iff $d(\ar_3) = 1 ∧ \ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop$. 
%	\item Define $\nwibeatse[\prop]_{(1)}$ as $\ar_3 \nwibeatse[\prop]_{(1)} \ar_2$ iff $d(\ar_3) = 1 ∧ \ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstope \prop$. 
	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff, first, $d(\ar_3) = k+1$, and second, $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$. Proceed similarly for $\nwibeatse[\prop]_{(k+1)}$.
	\item Define $\wibeatse[\prop] = \bigcup_{k ≥ 0} \wibeatse[\prop]_{(k)}$, and similarly for $\nwibeatse[\prop]$.
\end{itemize}

@@

\section{Conditions}
All these conditions assume that a decision situation $(\allalts, \allargs, \{\ibeatse[\prop]\}, \{\ibeatse[\prop, \text{sure}]\})$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.

Define $\argsdec = \clargs \setminus \text{im}(\wibeatse)$ the decisive arguments according to $\wibeatse$, or $\wibeatse$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv(\ar) = \emptyset$.

\begin{definition}[Reinstatement]
	Given $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3 \in \argsdec$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive. This should not invalidate the conditions, but it does currently. But it’s not a problem: the model would actually not be built this way. In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned. Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$. Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice). We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement). Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.}
\end{definition}

\begin{definition}[Justifiable unstability]
	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse \ar_1, \ar_2 \nwibeatse \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
\end{definition}

\begin{definition}[Finite defense]
	If $\wibeatseinv(\ar) \subseteq \wibeatse(\argsdec)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check). But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
\end{definition}
Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.

Define $R$, the reinstates relation, as follows: $\ar_3 R \ar_1$ iff $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$ (for some $\ar_2$), $\ar_3 \in \argsdec$. Define $\gdargs$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R$.
\begin{definition}[Covering]
	$\forall \ar \in \gdargs, \ar' \in \allargs: \ar' \ibeatse \ar ⇒ \ar' \mbeats \ar$. \footnote{Specify $\ibeatse$.}
\end{definition}

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$. Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: \ar_1 \ibeatse[\prop] \ar$.
	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits). Thus we only need to prove $\prop \notin \iposs$, for which $\ar_1 \ibeatse[\prop] \ar$ suffices.}
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$. Furthermore, if $¬\prop \in \mleadsto(\clargs) ∧ \prop \notin \mleadstoinv(\clargs)$, $¬\prop \in \isure$.
\end{theorem}
\begin{proof}
$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.

First, we want to prove that $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.

By hypothesis, $\wibeatseinv(\ar_1) \subseteq \wibeatse(\argsdec)$. Thus, $\exists \args \subseteq \argsdec \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse(\args)$, $\args$ finite [Finite defense].

>>>>

\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=14pt, a4paper, french, english]{scrartcl}
\input{preamble/packages}
\input{preamble/math_basics}
\input{preamble/math_mine}
\input{preamble/redac}
\input{preamble/draw}
\input{preamble/acronyms}
\addtokomafont{labelinglabel}{\sffamily\bfseries}

\begin{document}
\title{Simple models of deliberated preference}
\author{Olivier Cailloux}
\affil{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 PARIS, FRANCE\\
	\href{mailto:olivier.cailloux@dauphine.fr}{olivier.cailloux@dauphine.fr}
}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

@@

@@

We define $(\ar, \ar') \ileadstopst \prop ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, $(\ar, \ar') \ileadstosst ¬\prop ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$, $(\ar, \ar') \ileadstose ¬\prop ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\} ⇔ ¬((\ar, \ar') \ileadstopst \prop)$, and $(\ar, \ar') \ileadstope \prop  ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\} ⇔ ¬((\ar, \ar') \ileadstosst ¬\prop)$.

TODO do everything with only one relation. Define for each prop: $\prop^{s}$ and $\prop^p$, and define $¬(\prop^s) = (¬\prop)^p$, and we can do everything with $(\ar, \ar') \ileadsto \prop^p$ (defined as $\ileadstopst \prop$) and $(\ar, \ar') \ileadsto \prop^s$ (defined as $\ileadstosst \prop$).

Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.} 
and (A2) that $\ileadstosst \subseteq \ileadstopst$
\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
the pair $(\ar, \ar')$ being understood as unordered (thus not different than $(\ar', \ar)$).

@@

We say that a situation is $(\prop, ¬\prop)\text{-unstable}$ iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
\footnote{Example of $(\prop, ¬\prop)\text{-unstable}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}

\begin{theorem}
	$\prop \notin \iposs ∧ ¬\prop \notin \iposs ⇔ (\prop, ¬\prop)\text{-unstable}$.
\end{theorem}
The proof follows from \cref{ft:notposs}.

\begin{theorem}
	$\prop \in \isure ⇒ ¬\prop \notin \iposs$.
\end{theorem}
This is because some $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).

@@

\begin{definition}[Clear-cut]
	A situation is $\prop$-clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$. A situation is $(\prop, ¬\prop)$-clear-cut iff $\prop \notin \isure ∧ ¬\prop \notin \isure ⇒ \prop \in \iposs ∧ ¬\prop \in \iposs$.
\footnote{$\prop\text{-CC} ∧ ¬\prop\text{-CC} ⇔ (¬\prop \in \isure ∨ \prop \in \iposs) ∧ (\prop \in \isure ∨ ¬\prop \in \iposs) ⇔ (¬\prop \in \isure ∧ \prop \in \isure) ∨ (¬\prop \in \isure) ∨ (\prop \in \isure) ∨ (\prop \in \iposs ∧ ¬\prop \in \iposs) ⇔ (\prop, ¬\prop)\text{-CC}$.}
\footnote{$\overline{\prop\text{-CC}} ∧ \overline{¬\prop\text{-CC}} ⇔ (\prop, ¬\prop)$-unstability.}
\footnote{Example of $\overline{¬\prop\text{-CC}} ∧ \prop \in \iposs$ (thus with $\prop\text{-CC}$ and no $(\prop, ¬\prop)$-unstability): $\forall (\ar, \ar'), (\ar, \ar') \ileadstose \prop, (\ar, \ar') \ileadstope ¬\prop, (\ar, \ar') \ileadstopst \prop$. In such a situation, it is unclear whether $\prop$ holds rather than $¬\prop$ or both $\prop$ and $¬\prop$.}
\footnote{Hence (with possible meaning merely possible and not sure), for a given pair $(t, ¬t)$, either both are possible, or one is sure, or only $¬\prop$-CC and $¬t \in \iposs$ and $t \notin \iposs$, or only $\prop$-CC and $t \in \iposs$ and $¬t \notin \iposs$, or no CC and $(\prop, ¬\prop)$-unstable.}
\footnote{Something like Axiom JU should be sufficient for CC. We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$. JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive. Means that if not CC, then not JU. Hence, infinite discussion happens, or irreducible unstability. Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.}
\end{definition}

$\prop$ is provably possible, $\prop \in \ipposs$, iff $\prop \in \iposs ∧ ¬\prop\text{-CC}$.
\footnote{$\prop \in \ipposs ⇔ \prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC}$ (because $\prop \in \iposs ⇒ \prop\text{-CC}$).}
\footnote{
\begin{itemize}
	\item $\prop \in \ipposs ∧ ¬\prop \in \ipposs ⇔ \prop \in \iposs ∧ ¬\prop \in \iposs ⇔ \prop \in \iposs ∧ ¬\prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC} ⇔ \prop \notin \isure ∧ ¬\prop \notin \isure ∧ (\prop, ¬\prop)\text{-CC}$
	\item $\prop \in \ipposs ∧ ¬\prop \notin \ipposs ⇔ \prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC} ∧ ¬\prop \notin \iposs ⇔ \prop \in \isure$
	\item $\prop \notin \ipposs ∧ ¬\prop \notin \ipposs ⇔ \overline{\prop\text{-CC}} ∨ \overline{¬\prop\text{-CC}}$.
\end{itemize}
}

\section{Models}
A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the following constraints.

@@

Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
$\mbeats(\args)$: arguments that $\args$ attacks, $\ar_1 \in \mbeats(\args) ⇔ \exists \ar_2 \in \args \suchthat \ar_2 \mbeats \ar_1$; $\mbeatsinv(\ar)$: arguments attacking $\ar$, $\ar_2 \in \mbeatsinv(\ar) ⇔ \ar_2 \mbeats \ar$.

Given a decision situation, we define the relations $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ in order to obtain the following result.

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ (\ar_3, \ar_2) \ileadstope ¬\prop$.}

@@

This is done with the following construction.
Given a model. 
\begin{itemize}
	\item Define a root as an argument that $\mbeats$-attacks nothing. 
	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$. \footnote{Thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on.} 
	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. 
	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$. Proceed similarly for $\nwibeatse[\prop]_{(k+1)}$.
	\item Define $\wibeatse[\prop] = \bigcup_{k ≥ 0} \wibeatse[\prop]_{(k)}$, and similarly for $\nwibeatse[\prop]$.
\end{itemize}

@@

\section{Conditions}
All these conditions assume that a decision situation $(\allalts, \allargs, …)$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.

Define $\argsdec^\prop = \clargs \setminus \text{im}(\wibeatse[\prop])$ the decisive arguments according to $\wibeatse[\prop]$, or $\wibeatse[\prop]$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv[\prop](\ar) = \emptyset$.

\begin{definition}[Reinstatement]
	Given $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1, \ar_3 \in \argsdec^\prop$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive. This should not invalidate the conditions, but it does currently. But it’s not a problem: the model would actually not be built this way. In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned. Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$. Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice). We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement). Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.}
	\footnote{Is Reinf equivalent to Justifiable unstability? Define $\ar_3 \wibeatsst[\prop] \ar_2 ⇔ \ar_3 \wibeatse[\prop] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\prop] \ar_2)$. Prove that $\ar_3 \wibeatsst[\prop] \ar_2 \wibeatse[\prop] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\prop] \ar_3 + \ar_1)$.} 
\end{definition}

\begin{definition}[Justifiable unstability]
	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\prop] \ar_1, \ar_2 \nwibeatse[\prop] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
\end{definition}

$\ar$ is $\prop$-defended iff $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$ (its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments).

\begin{definition}[Finite defense]
	If $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\prop](\args)$.
\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check). But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
\end{definition}
Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.

Define $R^\prop$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\prop \ar_1$ iff $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1$ (for some $\ar_2, \prop$), $\ar_3 \in \argsdec^\prop$. Define $\gdargs^\prop$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R^\prop$. Given $\prop, \ar \in \gdargs^\prop, \ar' \in \allargs$, define $\ar' \ibeatse[\prop] \ar ⇔ (\ar', \ar) \ileadstose ¬\prop$.
\begin{definition}[Covering]
	$\forall \prop, \ar \in \gdargs^\prop, \ar' \in \allargs: \ar' \ibeatse[\prop] \ar ⇒ \ar' \mbeats \ar$. 
\end{definition}

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$. Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: (\ar_1, \ar) \ileadstose ¬\prop$.
	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits). Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$ suffices.}
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$. Furthermore, if $¬\prop \in \mleadsto(\clargs) ∧ \prop \notin \mleadstoinv(\clargs)$, $¬\prop \in \isure$.
\end{theorem}
\begin{proof}
First, we want to prove that $\ar_1$ $\prop$-defended implies $\ar_1$ replaceable by some $\wibeatse[\prop]$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.

Because $\ar_1$ is $\prop$-defended, $\exists \args \subseteq \argsdec^\prop \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\prop](\args)$, $\args$ finite [Finite defense].
